---
title: "Export simulation to C++"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Export simulation to C++}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package

```{r exportSimulation}
library(ospsuiteCpp)
# Load simulation
simFilePath <- system.file("extdata", "Aciclovir.pkml", package = "ospsuite")
sim <- loadSimulation(simFilePath)
par <- c("Aciclovir|Lipophilicity",
         "Aciclovir|Fraction unbound (plasma)")
# select free parameter, export and compile
opt = SimulationBatchOptions$new(variableParameters = par, variableMolecules = NULL)
cppFile = exportSimulationCpp(sim, opt, outputName = "Aciclovir")
dllFile = compileSimulationCpp(cppFile)

# initialize simulation, run once with the default paramter, change time grid and parameter and run again
sim = SimulationCompiled$new('Aciclovir')
parameter = sim$getP()
res1 = sim$run(parameter)
tgrid = sim$getT()
sim$setT(c(tgrid, tgrid[length(tgrid)]+1.0))
parameter[1] = parameter[1] + 0.1
res2 = sim$run(parameter)

```
The value `-1` for the sensitivity of "AUC_inf" of the output `Organism|PeripheralVenousBlood|Aciclovir|Plasma (Peripheral Venous Blood)` for the parameter `Organism-Kidney-Volume` means that increasing `Organism-Kidney-Volume` by 10% will decrease "AUC_inf" by 10%.
Note that the list of sensitivities is ordered from largest to smallest with respect to magnitude.

## Import and export of sensitivity analysis results
Sensitivity analysis calculated in R can be exported to a *.csv file, which can be loaded in another instance.

```{r SAExport}
# Load and run the simulation
simFilePath <- system.file("extdata", "simple.pkml", package = "ospsuite")
sim <- loadSimulation(simFilePath)
simulationResults <- runSimulation(simulation = sim)

# Create a `SensitivityAnalysis` with all constant parameters and run it
sa <- SensitivityAnalysis$new(simulation = sim)
saResult <- runSensitivityAnalysis(sa)

# Export to csv
saResultPath <- system.file("extdata", "SAResult.csv", package = "ospsuite")
exportSensitivityAnalysisResultsToCSV(results = saResult, filePath = saResultPath)

# Load from csv
saResultLoaded <- importSensitivityAnalysisResultsFromCSV(filePaths = saResultPath, simulation = sim)
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
